---
title: "graph isomorphism"
author: "Jonathan Bourne"
date: "09/04/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---


There are two major areas that need clarification

1: Why does SETSe_data_prep and SETSe_data_prep2 not give the same result?
  THis is obviously a coding issue. It is important obviously as the results need to be correct. and also because the v2 version is much faster for larger graphs. It also uses much less memory
  
  This differences appears to be soley due to different timestep settings. values were opposite signed as the system is probably oscillating.

2: Why are some topologically distinct graphs classed as identical? this is particularly the case with the latin squares
This get closer to the core of what SETSe does and where it is useful and where it is not.


One thing that may help is explicitly marking non matches instead of only marking matches.

#Setup
```{r}


packages <- c("tidyverse", "igraph","readr","readxl", "broom", "stringr", "xtable", "rlang", "latex2exp", "yardstick", "minpack.lm", "ggraph", "patchwork", "rsample", "VGAM", "class", "mclust")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

select <- dplyr::select
arrange <- dplyr::arrange
map <- purrr::map
sapply(packages, library, character.only = TRUE)

library(NetworkSpringEmbedding)

#Set up file system to read the correct folders
PLwd <- "/home/jonno/graph_isomorphism_data"
CodeFolder <- "/home/jonno/setse_isomorphism"
SubcodeFolder <- file.path(CodeFolder, "sub_code")


#Latex folders for figures tables etc
LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/setse_iso" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")

#Load some other useful functions
list.files("/home/jonno/Useful_PhD__R_Functions", pattern = ".R", full.names = T) %>%
  walk(~source(.x))


```



#Read first graph

r2 and t2 contain isomorphic pairs.
the others contain non-isomorphic pairs


##r2

These should all match the and show isomorphism
```{r}

file_path_r2 <- list.files(file.path(PLwd, 
                                  "Benchmark Graphs for Practical Graph Isomorphism", 
                                  "cfi-rigid-r2-tar/cfi-rigid-r2"), 
                        full.names = T )

r2_data_path <- file.path(PLwd, "Benchmark Graphs for Practical Graph Isomorphism/graph_type_data", "r2_data.rds")
if(file.exists(r2_data_path)){
  r2_data <- readRDS(r2_data_path)
} else{
  r2_data <- graph_iso_data_function(file_path_r2)
saveRDS(r2_data, r2_data_path )
  
}


embedded_pairs_r2 <-3:4 %>%
  map(~{
    
    graph_rank <- .x
    
    g <- read_graph(file = file_path_r2[.x], 
                    format = "dimacs",
                    directed = FALSE) %>%
  iso_spring_prep()
    
    temp <- auto_SETSe(g = g, 
                       force ="force",
                       flow = "flow",
                       distance = "distance",
                       capacity = "edge_capacity",
                       tstep = 0.01, 
                       tol = sum(abs(vertex_attr(g, "force")))/10000, 
                       mass = mean(abs(vertex_attr(g, "force"))),
                       hyper_max = 50000,
                       hyper_iters = 100,
                       hyper_tol = 0.001,
                       step_size = 0.1,
                       verbose = FALSE)
    
    temp %>% map(~{ .x %>% mutate(graph_id = basename(file_path_r2[graph_rank]))})
    
  }) %>%
  transpose %>%
  map(~bind_rows(.x))


embedded_pairs_r2$network_dynamics %>%
  ggplot(aes(x = Iter, y = static_force, colour = graph_id)) + geom_line()

#change the df structre to get the node elevations aligned
test <- embedded_pairs_r2$node_embeddings %>%
  select(elevation, graph_id) %>%
  arrange(elevation) %>%
  group_by(graph_id) %>%
  mutate(element_id = 1:n()) %>%
  ungroup %>%
  pivot_wider(names_from = graph_id, values_from = elevation) %>%
  rename(graph_a = 2, graph_b = 3)

#test for equality
all.equal(test$graph_a, test$graph_b)
    
test %>%
  ggplot(aes(x = element_id, y = graph_a)) + geom_point()


g_r2 <- read_graph(file = file_path_r2[3], 
                    format = "dimacs",
                    directed = FALSE)
##All nodes test, two identical graphs should be the same as testing each individual graph
r2_comparison <- 3:4 %>%
  map(~{
    g <- read_graph(file = file_path_r2[.x], 
                    format = "dimacs",
                    directed = FALSE)
    
    Out <- setse_complete_function(g)
    
    return(Out)
  })

test2 <- get_graph_matches(r2_comparison[[2]], r2_comparison[[2]])

test3 <- test2 %>%
  group_by(counts) %>%
  summarise(occurances = n())

g_r2 <- read_graph(file = file_path_r2[3], 
                    format = "dimacs",
                    directed = FALSE)  
g_r2 %>%
  ggraph()+  
  geom_edge_fan() +
      geom_node_point(aes(colour = factor(degree(g_r2))), size=3) +
     # scale_shape_manual(values=c(21, 24, 23)) +
      guides(fill = "none", shape = "none")


```

##d3


```{r}
    
    g <- read_graph(file = file_path[4], 
                    format = "dimacs",
                    directed = FALSE) %>%
  iso_spring_prep()

automorphisms(g)
set.seed(3)
g %>%
  ggraph()+  
  geom_edge_fan() +
      geom_node_point(aes(colour = factor(degree(g))), size=3) +
     # scale_shape_manual(values=c(21, 24, 23)) +
      guides(fill = "none", shape = "none")

```


```{r}

file_path_d3 <- list.files(file.path(PLwd, 
                                  "Benchmark Graphs for Practical Graph Isomorphism", 
                                  "cfi-rigid-d3-tar/cfi-rigid-d3"), 
                        full.names = T )


#check graphs
d3_data_path <- file.path(PLwd, "Benchmark Graphs for Practical Graph Isomorphism/graph_type_data", "d3_data.rds")
if(file.exists(d3_data_path)){
  d3_data <- readRDS(d3_data_path)
} else{
  d3_data <- graph_iso_data_function(file_path_d3)
saveRDS(d3_data, d3_data_path )
  
}


embedded_pairs_d3 <-c(33,34)%>%
  map(~{
    
    graph_rank <- .x
    
    g <- read_graph(file = file_path_d3[.x], 
                    format = "dimacs",
                    directed = FALSE) %>%
  iso_spring_prep() 
    
    g <- g %>%
      set.vertex.attribute(., "force", value =vertex_attr(g, "force")/( sum(abs(vertex_attr(g, "force")))/2)) %>%
      set.edge.attribute(., "k", value = ifelse(edge_betweenness(g)> mean(edge_betweenness(g)),100, 10)) %>%
    set.edge.attribute(., "distance", value = 100000)
 # print(automorphisms(g))
    temp <- auto_SETSe(g = g, 
                       force ="force",
                       flow = "flow",
                       distance = "distance",
                       capacity = "edge_capacity",
                       tstep = 0.1, 
                       tol = sum(abs(vertex_attr(g, "force")))/100000, 
                       mass = mean(abs(vertex_attr(g, "force"))),
                       hyper_max = 50000,
                       hyper_iters = 1000,
                       hyper_tol = 0.001,
                       step_size = 0.1,
                       verbose = TRUE)
    
    temp %>% map(~{ .x %>% mutate(graph_id = basename(file_path_d3[graph_rank]))
      })
    
  }) %>%
  transpose %>%
  map(~bind_rows(.x))

test <- embedded_pairs_d3$network_dynamics 
embedded_pairs_d3$network_dynamics %>%
  ggplot(aes(x = Iter, y = static_force, colour = graph_id)) + geom_line()

variable_name <- "elevation"

test <- embedded_pairs_d3$node_embeddings %>%
  select(elevation, graph_id) %>%
  arrange(elevation) %>%
  group_by(graph_id) %>%
  mutate(element_id = 1:n()) %>%
  ungroup %>%
  pivot_wider(names_from = graph_id, values_from = elevation) %>%
  rename(graph_a = 2, graph_b = 3) %>%
  mutate(diff = graph_a - graph_b)



cosine_mat(test$graph_a %>% as.matrix(), test$graph_b %>% as.matrix)

test <- embedded_pairs_d3$edge_embeddings %>%
  select(graph_id, tension) %>%
  arrange(tension) %>%
  group_by(graph_id) %>%
  mutate(element_id = 1:n()) %>%
  ungroup %>%
  pivot_wider(names_from = graph_id, values_from = tension) %>%
  rename(graph_a = 2, graph_b = 3)  %>%
  mutate(diff = graph_a == graph_b)

#test for equality
all.equal(test$graph_a, test$graph_b)


embedded_pairs_d3 %>%
  ggplot(aes(x = edge_name, y = tension, colour = graph_id))+ geom_point()

ggplot(test, aes(x = element_id, y = graph_a)) +geom_point()

```


#all nodes test

```{r}
g <- read_graph(file = file_path_d3[2], 
                    format = "dimacs",
                    directed = FALSE)

betweenness(g)

d3_comparison <- 3:4 %>%
  map(~{
    g <- read_graph(file = file_path_d3[.x], 
                    format = "dimacs",
                    directed = FALSE)
    
    Out <- setse_complete_function(g)
    
    return(Out)
  })

test2 <- get_graph_matches(d3_comparison[[1]], d3_comparison[[2]])

test3 <- test2 %>%
  group_by(counts) %>%
  summarise(occurances = n())


set.seed(3)
g %>%
  ggraph()+  
  geom_edge_fan() +
      geom_node_point(aes(colour = factor(degree(g))), size=3) +
     # scale_shape_manual(values=c(21, 24, 23)) +
      guides(fill = "none", shape = "none")

```


#NAUTY benchmarks

appears to solve the automorphisms of the following series'
ag, latin square, lattice, k


does not appear to solve the following series
latin square switched edge,

multicomponent, so haven't tried
KEF

I don't understand why some graphs it is fine to find automorphisms and others not.

##ag series

This works up to 19 but not at 23, why? Does the system explode? setting a variable time period makes it much slower suggesting that the system is managing to diverge in less steps than it takes to cross the network.


```{r}

NAUTY_ag <-"/home/jonno/graph_isomorphism_data/NAUTY benchmarks/undirected_dim/latin-sw/latin-sw"
#list.files("/home/jonno/graph_isomorphism_data/NAUTY benchmarks/undirected_dim/ag/ag", full.names = T, pattern = "-$")
g <- read_graph(file = list.files(NAUTY_ag, full.names = T, pattern = "10-8$"), 
                    format = "dimacs",
                    directed = FALSE)


g2 <- read_graph(file = list.files(NAUTY_ag, full.names = T, pattern = "10-10$"), 
                    format = "dimacs",
                    directed = FALSE)


automorphisms(g)
vcount(g)
ecount(g)
degree(g)
betweenness(g)
test_short <- setse_complete_function(g, max_iter =500)

test_short2 <- setse_complete_function2(g2, max_iter =50000)

test <- get_graph_matches(test_short, test_short)
table(test$counts)


test2 <-(abs(1-cosine_mat(test_short, test_short2)))

 test3 <-get_graph_matches(test2, test2)

as_tibble(test_short2) %>% mutate(node_1 = rownames(test_short2)) %>% 
  pivot_longer(cols = -node_1, names_to = "node_2", values_to = "values") %>%
ggplot(aes(x = node_1, y = node_2, fill = factor(values))) + 
  geom_raster()

set.seed(3)
g %>%
  ggraph()+  
  geom_edge_fan() +
      geom_node_point(aes(colour = factor(degree(g))), size=3) +
     # scale_shape_manual(values=c(21, 24, 23)) +
      guides(fill = "none", shape = "none")
vcount(g)


gcd <- function(x,y) {
  r <- x%%y;
  return(ifelse(r, gcd(y, r), y))
}

gcd(121
  ,132)

  
  full_list <- vertex_attr(g,"label") %>%
    map(~{
      print(.x)
      node_id <- .x
      temp_g <- iso_complete_spring_prep(g, target_name = .x)
      
      temp <- SETSe2(temp_g, 
                    force ="force",
                    flow = "flow",
                    distance = "distance",
                    capacity = "edge_capacity",
                    edge_name = "edge_name",
                    k ="k",
                    tstep = 0.1/vcount(g), 
                    mass = mean(abs(vertex_attr(temp_g, "force"))), 
                    max_iter =5e5,#vcount(g)*2 , 
                    coef_drag = 1, 
                    tol = sum(abs(vertex_attr(temp_g, "force")))/10000,
                    sparse = sparse,
                    two_node_solution = FALSE,
                    include_edges = TRUE,
                    sample = 1)
      
      
      
      
      temp %>% map(~{ .x %>% mutate(node_id = node_id)})
      
    })

  
  #extract only the elevation data from the embedding
  Out <- 1:length(full_list) %>% map(~{
    full_list[[.x]]$node_embeddings %>%
      select(elevation) %>%
      arrange(-elevation)
  }
  ) %>%
    bind_cols %>%
    as.matrix()
  
    Out2 <- 1:length(full_list) %>% map(~{
    full_list[[.x]]$edge_embeddings %>%
      select(tension) %>%
      arrange(-tension)
  }
  ) %>%
    bind_cols %>%
    as.matrix()
      
      
temp$network_dynamics %>%
  ggplot(aes(x = t, y = static_force)) + geom_line()

temp$node_embeddings %>%
  ggplot(aes(x = node, y = elevation)) + geom_point()

temp$edge_embeddings %>%
  ggplot(aes(x = edge_name, y = tension)) + geom_point()



test_nodes <- get_graph_matches(Out, Out)
table(test_nodes$counts)

test_edges <- get_graph_matches(Out2, Out2)
table(test_edges$counts)

tests <- temp$edge_embeddings

table(Out2[,20])
table(temp$edge_embeddings$tension)
table(temp$node_embeddings$elevation)

#create an adjacency matrix with node order by elevation and ties broken by the col/row sum of tension?
```

#MIVIA

This loads data from the MIVIA dataset
```{r}
binary_folder <-"/home/jonno/graph_isomorphism_data/graphsdb/iso_m2Dr2/iso/m2D/m2Dr2"


#This is an iso morphic fraph small suize, with 16 nodes and is the A graph (first) of series 00
binary_files <- list.files(binary_folder, full.names = T, pattern = "iso_m2Dr2_s16.A01")

load_mivia <- function(file_path, n = 10000){
  
  #The n value
  file_dat <-readBin(con = file_path, what = "int", size = 2 , n= n, #signed = TRUE,
                     endian = "little")
  
  
  total_nodes <- file_dat[1]
  
  Adj <- matrix(rep(0, total_nodes^2), nrow = total_nodes)
  
  i <-2
  node_number <- 1
  while(i < length(file_dat)){
    
    
    number_of_edges <- file_dat[i]
    
    # print(paste0("node ", node_number, ", i ", i, ", total edges ", number_of_edges))
    
    
    if(number_of_edges>0){
      # print((i+1):(i+number_of_edges))
      edge_links <- file_dat[(i+1):(i+number_of_edges)] + 1 #the nodes are indexed to 0
      
      #print(edge_links)
      Adj[node_number, edge_links] <-1
    }
    
    node_number <- node_number + 1 # The next 
    i <- i + number_of_edges +1
  }

  g <- as.data.frame(which(Adj==1, arr.ind = T)) %>%
  graph_from_data_frame(., directed = FALSE)
  
return(g)    
  
}

test1 <- load_mivia(file_path = list.files(binary_folder, full.names = T, pattern = "iso_m2Dr2_s16.A00"))
test2 <- load_mivia(list.files(binary_folder, full.names = T, pattern = "iso_r005_m200.B50"))

vcount(test2)
ecount(test2)

test1 %>% automorphisms()
  plot

test1 %>% plot

length(test)

```



#Latin square test

There are some pretty wierd results going on at the moment. 
I am going to do a test with a simple latin square and a latin square with some of the edges changed to see what happens.


It may be possible to set the distance, time step and force as a function of the nodes and edges such that after d+1 time steps the height of the nodes is not minimal and so the difference between two equally sized graph is not smaller than the machine double epsilon resolution

```{r}

base_square <-matrix(1:9, nrow = 3, byrow = T)

latin_square <- matrix(0, nrow = 9, ncol = 9)
colnames(latin_square) <- 1:9

base_square

for( i in 1:9){
  
  row_col_id <-which(base_square ==i, arr.ind = T)
  
  latin_square[i,base_square[,row_col_id[,2]]] <- 1
  
  latin_square[base_square[row_col_id[,1],],i] <- 1
  
  
}

diag(latin_square) <- 0


g_latin <- graph_from_adjacency_matrix(latin_square, mode = "undirected")

latin_square_sw <- latin_square

latin_square_sw[1,2] <- 0
latin_square_sw[2,1] <-0

latin_square_sw[1,5] <- 1
latin_square_sw[5,1] <-1

latin_square_sw[5,6] <- 0
latin_square_sw[6,5] <- 0

latin_square_sw[2,6] <- 1
latin_square_sw[6,2] <- 1

latin_square_sw2 <- latin_square_sw

latin_square_sw2[4,5] <- 0
latin_square_sw2[5,4] <- 0

latin_square_sw2[4,8] <- 1
latin_square_sw2[8,4] <-1

latin_square_sw2[8,9] <- 0
latin_square_sw2[9,8] <- 0

latin_square_sw2[5,9] <- 1
latin_square_sw2[9,5] <- 1



#create the latin sqaure with 
g_latin_sw <- graph_from_adjacency_matrix(latin_square_sw, mode = "undirected")
g_latin_sw2 <- graph_from_adjacency_matrix(latin_square_sw2, mode = "undirected")

vcount(g_latin)
vcount(g_latin_sw)
vcount(g_latin_sw2)

ecount(g_latin)
ecount(g_latin_sw)
ecount(g_latin_sw2)

degree(g_latin)
degree(g_latin_sw)
degree(g_latin_sw2)

#the only change is betweeness
betweenness(g_latin)
betweenness(g_latin_sw)
betweenness(g_latin_sw2)

diameter(g_latin)
diameter(g_latin_sw)
diameter(g_latin_sw2)

#The squares match for small numbers of iterations but not when the iterations become large.
#This doesn't make any sense, they should not match for all values 
#It is worth checking the strain and dynamics of the system
test <- setse_complete_function(g_latin, max_iter =vcount(g_latin)*10, name_attr = "name")
test_v1
test2 <- setse_complete_function(g_latin_sw, max_iter =vcount(g_latin_sw)*10, name_attr = "name")

test3 <- setse_complete_function(g_latin_sw2, max_iter =vcount(g_latin_sw2)*10, name_attr = "name")

#Also the matches change dependent of which way round you test. 
#It is wierd and seems wrong
test_out <- get_graph_matches(test2, test)

abs(1-cosine_mat(test, test)) <= .Machine$double.eps

set.seed(3)
g_latin_sw2 %>%
  ggraph()+  
  geom_edge_fan() +
      geom_node_point( size=3) +
     # scale_shape_manual(values=c(21, 24, 23)) +
      guides(fill = "none", shape = "none")


#find appropriate parameters for the graphs using autosetse

parameter_test <- 1:3 %>% map(~{

  g <- list(g_latin, g_latin_sw, g_latin_sw2)[[.x]]
  
  graph_type <- c("latin", "latin_sw","latin_sw2")[.x]
  
  full_list <- 1 %>%
    map(~{
      print(.x)
      node_id <- .x
      temp_g <- iso_complete_spring_prep(g, target_name = .x) %>%
        set.edge.attribute(., "distance", value = 1)
      
      temp <- auto_SETSe(temp_g, 
                    force ="force",
                    flow = "flow",
                    distance = "distance",
                    capacity = "edge_capacity",
                    edge_name = "edge_name",
                    k ="k",
                    tstep =0.1, 
                    mass = mean(abs(vertex_attr(temp_g, "force"))), 
                    max_iter = 1e5, 
                    tol = 0,#sum(abs(vertex_attr(temp_g, "force")))/50000,
                    hyper_tol = 0.001,
                    verbose = T
                   ) 
      
    }) %>% transpose %>%  map(~{.x %>% bind_rows() %>% mutate(#node_id = node_id,
                                    graph = graph_type)})
  
  
}) %>% transpose %>%  map(~{.x %>% bind_rows()})


parameter_test$network_dynamics %>%
  ggplot(aes(x = log10(Iter), y = log10(static_force), colour = graph)) + geom_line()

parameter_test$memory_df %>%
    ggplot(aes(x = common_drag_iter, y = error, colour = graph)) + geom_line()

#one vs all for all three graphs
test_expanded <- 1:3 %>% map_df(~{

  g <- list(g_latin, g_latin_sw, g_latin_sw2)[[.x]]
  
  graph_type <- c("latin", "latin_sw","latin_sw2")[.x]
  
  full_list <- vertex_attr(g,"name") %>%
    map_df(~{
      print(.x)
      node_id <- .x
      temp_g <- iso_complete_spring_prep(g, target_name = .x)  %>%
        set.edge.attribute(., "distance", value = 1)
      
      temp <- SETSe_expanded(temp_g, 
                    force ="force",
                    flow = "flow",
                    distance = "distance",
                    capacity = "edge_capacity",
                    edge_name = "edge_name",
                    k ="k",
                    tstep =0.1, 
                    mass = mean(abs(vertex_attr(temp_g, "force"))), 
                    max_iter = 50e4, 
                    coef_drag = 12, 
                    tol = sum(abs(vertex_attr(temp_g, "force")))/100000,
                    sparse = FALSE,
                    two_node_solution = FALSE#,
                   # include_edges = TRUE,
                   # sample = 1
                   ) %>% mutate(node_id = node_id,
                                    graph = graph_type)
      
    })# %>% transpose# %>%  map(~{.x %>% bind_rows()})
  
  
})# %>% transpose %>%  map(~{.x %>% bind_rows()})

automorphisms(g_latin)
automorphisms(g_latin_sw)
automorphisms(g_latin_sw2)

test_expanded %>%
  filter((Iter %% 1)==0,
        Iter<100,
         node_id ==5
         ) %>%
  ggplot(aes(x = Iter, y = elevation, colour = factor(graph))) +geom_line() +
  facet_wrap(~node)


test_expanded %>%
  filter((Iter %% 1)==0,
#         Iter<1000,
         node_id ==5
         )

#This graph shows that SETse can distinguish between different graphs
#and also shows the resolution problem

test_expanded %>%
  filter((Iter %% 1)==0,
         Iter<100,
  #       node_id ==8
         ) %>%
  group_by(graph, Iter, node_id) %>%
  summarise_if(is.numeric, ~mean(abs(.))) %>%
  ggplot(aes(x = Iter, y = elevation, colour = graph))+ geom_line() +
  facet_wrap(~node_id)+
  coord_cartesian(y = c(0.32, 0.37), x = c(40, 100)) +
  labs(title = "Mean absolute node elevation, by focal node and graph type, for\nlatin square n= 3 and variants",
       x = "Iterations in thousands") +
  theme(axis.text.x = element_text(angle = 45))


test <- test_expanded %>%
  filter(#(Iter %% 10)==0,
         Iter<100,
  #       node_id ==8
         ) %>%
  arrange(graph) %>%
  group_by(Iter, node_id, node) %>%
  summarise_if(.,is.numeric, ~log10(first(.)+1)-log10(last(.)+1))

# %>%
#  summarise_if(.,is.numeric, ~first(.)-last(.))


test2 <-test_expanded %>%
  filter(
    (Iter %% 10)==0,
    Iter <=2000,
    graph != "latin_sw2") %>%
  arrange(graph) %>%
  group_by(Iter, node_id, node) %>%
  summarise_if(.,is.numeric, ~log10(first(.)+1)-log10(last(.)+1))

test %>%
  ggplot(aes(x = Iter, y = log10((elevation)), colour = as.factor(node))) + geom_line()+
  facet_wrap(~node_id)


test3 <- test2 %>%
  filter(Iter ==200)

```

